\large Neural and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-09-12 docs/papers/sto/so.tex
FIXUP draft minor

@@

We perform distributed data-parallel training using GPU devices hosted on
multiple CPU nodes.
% TODO hardware details
The training data samples are uniformly distributed to the processes, with
each process being binded to a single GPU device.
In each training step, a data sample is fed into the GPU from the CPU memory
where the preloading takes place to save the reading time from the disk.

>>>>

% hardware setups
We perform distributed data-parallel training using GPU devices hosted on
multiple CPU nodes.
With each process being binded to a single GPU device, the training data samples
are uniformly distributed to the processes.
In total, we use [...] \GPU\ GPUs, each accompanied with [...] CPU cores and
[...] GB CPU memory mainly for preloading the training data.
In each training step, a data sample is fed into the GPU from the CPU memory
where the preloading takes place to save the reading time from the disk.

@@
